---
title: "FinalProject"
author: "LingzhouAo"
date: "5/7/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Overview
As we all know, convenience is one of the most important factors that influences the house renting price, and obviously, in most cases, if a district is more convenient, the house renting price of this district will be higher. The price and number of restaurants play very important roles in determining whether a district is convenient, and also people cannot live without food, which means when people want to rent a so I decide to explore the relationship between house renting price and restaurant price range.
Because house renting and catering industry are very booming in Boston, I choose to use Boston as our study area.

The price and number of restaurants play a very important role in determining whether a district is convenient, and also people cannot live without food, so I decide to explore the relationship between house renting price and restaurant average customer spending.

## Get Data
1.	For house information, because the Zillow API doesn't support getting data in a wide range, I implement a web crawler to scrap data from Zillow.
2.	For restaurant information, I use Yelp API to get the data of restaurants.
3.	In order to know the exact location of houses and restaurants, I choose to use Google Map API to get the latitude and longitude of each house or restaurant. And also, because the size of data is larger than 2,500, I have to pay for the api. So I will stop this api after submitting this project to github.

##Deal with Data
The files houses.R and yelp.R are used to tidy those data I get from website. For yelp data,I turned the original symbol \$, \$\$, \$\$\$, \$\$\$ on Yelp into 1, 2, 3, 4 these four levels. Level one and two means relatively inexpensive\$ restaurants and \$$ restaurants, level three and four represents for the other two.
For houses data, I calculate the average price for each house and based on this price and its coordinate information, I use K-means to cluster the house data


##K-means Results

##Decide K value
```{r}
library(ggmap)
suppressMessages(library("tidyverse"))
library(magick)
library(ggplot2)

final <- read_csv("houses.csv")

df_final <- data_frame(price = final$price,
                      lat = final$lat,
                      lng = final$lng
)
yelp <- read_csv("YelpData.csv")
df_yelp <- data_frame(price = yelp$price,
                     lat = yelp$latitude,
                     lng = yelp$longitude
)

final.scale <- scale(df_final)

final.scale[,2] <- final.scale[,2] *5
final.scale[,3] <- final.scale[,3] *5

#Elbow Method for finding the optimal number of clusters
set.seed(123)
# Compute and plot wss for k = 2 to k = 15.
k.max <- 15
data <- final.scale
wss <- sapply(1:k.max, 
              function(k){kmeans(data, k, nstart=50,iter.max = 15 )$tot.withinss})
wss
plot(1:k.max, wss,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")

# Choose 10 as the number of cluters

k.m <- kmeans(data, 10, nstart = 50, iter.max = 15)

df_cluster <- data_frame(cluster = k.m$cluster)
new_final <- cbind(df_final, df_cluster)


price_label <- c(1:10)
lat_label <- c(1:10)
lng_label <- c(1:10)
for (i in c(1:10)){
  new_final$label[new_final$cluster == i] <- mean(new_final$price[new_final$cluster == i])
  price_label[i] <- mean(new_final$price[new_final$cluster == i])
  lat_label[i] <- mean(new_final$lat[new_final$cluster == i])
  lng_label[i] <- mean(new_final$lng[new_final$cluster == i])
}
price_label
lat_label
lng_label

new_final$new_label <- factor(new_final$label)
```
```{r}
register_google(key = 'AIzaSyAmOQseQL27vmpzc4Lpddmocrzv1jDkXwg')
map <- get_googlemap(center =c(-71.0589,42.3601), zoom = 11, maptype = "roadmap")
ggmap(map)

ggplot(data = new_final, aes(x = lng, y = lat , color = new_label), size = 5, shape = 21)+geom_point()
```
```{r}
ggmap(map)+
  geom_point(data = new_final,aes(x = lng, y = lat, color = new_label))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
##Merge Data
Then I want to related restaurants data with house data, so I put each restaurant into its nearest cluster. After that, I can analyze the relationship between them.

##Results
```{r}
row.has.na <- apply(df_yelp, 1, function(x){any(is.na(x))})
sum(row.has.na)

df_yelp <- df_yelp[!row.has.na,]

label_lat <- k.m$centers[,2]
label_lng <- k.m$centers[,3]

yelp_scale <- scale(df_yelp)
yelp_lat <- yelp_scale[,2]*5
yelp_lng <- yelp_scale[,3]*5

r_label <- c(1:943)

for (i in c(1:943)){
  r_l_x <- yelp_lat[i]
  r_l_y <- yelp_lng[i]
  l <- 1
  d <- (r_l_x - label_lat[1])**2 + (r_l_y - label_lng[1])**2
  for (j in c(2:10)){
    new_d <- (r_l_x - label_lat[j])**2 + (r_l_y - label_lng[j])**2
    if (d > new_d){
      l <- j
      d <- new_d
    }
  }
  r_label[i] <- price_label[l]
}

new_df_yelp <- cbind(df_yelp,r_label)
names(new_df_yelp)[4] <- paste("house_price")


ggplot(data = new_df_yelp, aes(x = house_price, y = price, color = price))+geom_point()
```
```{r}
library(plyr)
fre_1 <- count(new_df_yelp,"house_price")

ggplot(data = fre_1,aes(x = house_price, y = freq))+geom_line()
```

##Summary
First, by observing the clustering result on google map, I think the result is quite realiable based on the information we know about the house price of Boston and I put each restaurant into the nearest cluster. The point figure shows for each cluster which price level's restaurant it contains and the line figure shows for each cluster how many restaurants it contains. And based on the results, I figure out for those higest price level restaurants, they will choose the high house price area but not the highest beacause they want to attract as many target customers as they can but also they don't want to pay too much renting fee. For those low price level restaruants, they are everywhere, so I guess some of them are fast food restaurants. Everyone needs fast food. 
Therefore, based on the map that shows the distribution of house price, you can choose the best place for dinning to live."







