---
title: "Assignment3"
author: "LingzhouAo"
date: "4/1/2018"
output: pdf_document
---

#load data
```{r}
library(shiny)
library(readr)
A2010 <- read.csv( "bp appre 2010.csv", header = TRUE, stringsAsFactors = FALSE)

A2017 <- read.csv("bp appre 2017.csv", header = TRUE, stringsAsFactors = FALSE)

A2000.2017 <- read.csv("PB monthly summaries.csv", header = TRUE, stringsAsFactors = FALSE)
```

#clean data of BP Apprehensions 2010
```{r}
rownames(A2010)<-A2010[,1]

A2010 <- subset(A2010, select= -c(Sector))

A2010 <- rbind(A2010, colSums(A2010))

rownames(A2010) <- c(rownames(A2010)[-length(rownames(A2010))], "Total")
```

## cbind rowSums to dataframd
```{r}
A2010 <- cbind(A2010,rowSums(A2010))
```

## rename last column "Totals
```{r}
colnames(A2010) <- c(colnames(A2010)[-length(colnames(A2010))], "Total")
```

#clean data of BP Apprehensions 2017
```{r}
rownames(A2017) <- A2017[,1]

A2017 <- subset(A2017, select= -c(Sector))

A2017 <- rbind(A2017, colSums(A2017))

rownames(A2017) <- c(rownames(A2017)[-length(rownames(A2017))], "Total")
```

## cbind rowSums to dataframd
```{r}
A2017 <- cbind(A2017,rowSums(A2017))
```

## rename last column "Totals
```{r}
colnames(A2017) <- c(colnames(A2017)[-length(colnames(A2017))], "Total")
```

#statistics
```{r}
A2010_sector_mean <- apply(A2010[,1:12],1,mean)
A2010_sector_mean

A2010_month_mean <- apply(A2010[1:9,],2,mean)
A2010_month_mean

A2017_sector_mean <- apply(A2017[,1:12],1,mean)
A2017_sector_mean

A2017_month_mean <- apply(A2017[1:9,],2,mean)
A2017_month_mean

sector<-cbind(A2010_sector_mean,A2017_sector_mean)
```

#The maximum sector in 2010 is Tucson and the maximum sector in 2017 is Tio Grande Valley
```{r}
sector2010<-as.data.frame(t(A2010[1:9,]))
as.character(colnames(sector2010))
sector2010

sector2017<-as.data.frame(t(A2017[1:9,]))
as.character(colnames(sector2017))
sector2017

t.test(sector2010$Tucson,sector2017$`Rio Grande Valley`)

month<-cbind(A2010_month_mean,A2017_month_mean)
```

#The maximum three months in 2010 are March, April and May
```{r}
month2010<-as.data.frame((A2010[1:9,6:8]))
as.character(rownames(month2010))
month2010
month2010$sum<-apply(month2010,1,sum)
```

#The maximum three months in 2017 are October, November and December
```{r}
month2017<-as.data.frame((A2017[1:9,1:3]))
as.character(rownames(month2017))
month2017
month2017$sum<-apply(month2017,1,sum)
t.test(month2010$sum,month2017$sum)

new_A2000.2017 <- apply(t(A2000.2017[,2:13]),1,rev) 
ts <- as.vector(t(new_A2000.2017))
ts
ts2 <- ts(ts,frequency = 13,start = c(2000,10))
ts2
new_A2000.2017_mean <- apply(new_A2000.2017,1,mean)
new_A2000.2017_mean
ts.plot(ts2, gpars=list(xlab="year", ylab="Apprehensions", lty=c(1:3)))
```

#shiny app

```{r}
options(shiny.sanitize.errors = FALSE)
ui <- fluidPage(
  titlePanel("Assignment3 Plots"),
  
  sidebarLayout(position = "left",
                sidebarPanel("Check box",
                             checkboxInput("comparebysector", 
                                           "compare by sector", 
                                           value = T),
                             checkboxInput("comparebymonth", 
                                           "compare by month", 
                                           value = T),
                             checkboxInput("timeseries", 
                                           "time series", 
                                           value = T)
                ),
                mainPanel("Main panel",
                          fluidRow(
                            splitLayout(cellWidths = c("50%", "50%"), 
                                        plotOutput("graph1"), 
                                        plotOutput("graph2"))
                          ),
                          tabsetPanel(
                            
                            tabPanel("Compare by sector", plotOutput("graph3")),
                            tabPanel("Compare by month", plotOutput("graph4")),
                            tabPanel("time series", plotOutput("graph5")),
                            tabPanel("T-Test", textOutput("ttest")),
                            
                            p()
                          )
                          
                )
                
  ))


server <- function(input, output) {
  set.seed(1234)
  pt3 <- reactive({
    if(input$comparebysector){
      return(barplot(t(sector),
                     beside = TRUE,
                     legend.text = c("2010","2017"),
                     main = "compare by sector"))
    }
    else{
      return(NULL)
    }
  })
  
  pt4 <- reactive({
    if(input$comparebymonth){
      return(barplot(t(month),
                     beside = TRUE,
                     legend.text = c("2010","2017"),
                     main = "compare by month"))
    }
    else{
      return(NULL)
    }
  })
  
  pt5 <- reactive({
    if(input$timeseries){
      return(ts.plot(ts2,gpars = list(xlab="year",ylab="appre")))
    }
    else{
      return(NULL)
    }
  })
  
  output$graph1 <- renderPlot({
    barplot(A2017[1:9,13], names.arg = rownames(A2017)[1:9], 
            las=2,
            axisnames=TRUE,
            main="2017 Border Patrol Apprehensions by Sector",
            border="blue",
            col="red")
  })
  output$graph2 <- renderPlot({
    barplot(A2010[1:9,13], names.arg = rownames(A2010)[1:9], 
            las=2,
            axisnames=TRUE,
            main="2010 Border Patrol Apprehensions by Sector",
            border="blue",
            col="yellow")
  })
  
  output$graph3 <- renderPlot({pt3()})
  output$graph4 <- renderPlot({pt4()})
  output$graph5 <- renderPlot({pt5()})
    
  output$ttest <- renderPrint({
    return(t.test(month2010$sum,month2017$sum))
  })
}
```

# Run the application 
```{r}
shinyApp(ui = ui, server = server)
```

